\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-24 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
more rewriting

The past decade has seen rapid development in methodologies for forecasting time series that follow a hierarchical aggregation structure. Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted to ensure coherence with aggregation constraints. Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples. {\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating the problem as as an optimisation problem to minimises weighted squared errors between coherent and incoherent forecasts}.  The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model. In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation. This allows us to develop novel proofs and a clearer understanding of the interplay between forecast bias and reconciliation methods.

@@

In contrast to these methods, \citet{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as \emph{base} forecasts. Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment. A framework was proposed whereby the aggregation constraints were expressed in a regression model for the base forecasts. The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts. This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep[see for example][among others]{Athanasopoulos2009, AthEtAl2017, WicEtAl2019}. Some theoretical insight into the performance of forecast reconciliation methods has been provided by \citet{VanErven2015a} and \citet{WicEtAl2019}. Both papers provide a proof that reconciliation is guaranteed to improve base forecasts. The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method. This is optimal in the sense of minimising the trace of the reconciled forecast error covariance matrix under the assumption that the base forecasts are unbiased.

Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem. In this setting, we show that reconciled forecasts have a number of attractive properties when they are obtained via projections. We believe that this is clearer and more intuitive than explanations based on regression modelling. In addition to casting existing results in a new light, the geometric interpretation also allows us to derive three new important results.

First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints. As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling. Second, {\color{blue} we provide a new proof that for a given class of loss functions, reconciled forecasts can be found that dominate unreconciled forecasts. The projection that achieves this only depends on the loss function and not on the dependence in forecast errors. We believe that the link between a reconciliation method and loss function has not always been made clear in previous work that has dealt with this issue, for example \citet{VanErven2015a} and \citet{WicEtAl2019}}. Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.  {\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors, something that is targeted by the MinT method as well as newer methods found in \cite{NysEtAl2019}.  Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased. A natural question that arises is what to do in the case of biased reconciled forecasts. Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation. This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.

The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines hierarchical time series in a way that does not depend on any notion of bottom-level series. Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions {\color{blue}for} forecast reconciliation.

@@

In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.
\begin{itemize}
\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e. the base and reconciled forecasts should be `close'.  {\color{blue} This property is particularly emphasised by \cite{VanErven2015a} and \cite{NysEtAl2019}}
\item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.  {\color{blue} This property is particularly emphasised by \cite{WicEtAl2019}.}
\end{itemize}

To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast $\tilde{\bm{y}}$. A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$. {\color{blue} For Euclidean distance this can be expressed as minimising $\|\bm{S}\bm{G}\hat{\bm{y}}-\hat{\bm{y}}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.

The {\color{blue} second} property, that reconciliation should improve forecasts was touched upon in Section 2.3 of \citet{WicEtAl2019}. The discussion in that paper focuses on the case of MinT\@. Here we provide a new explicit proof of that result. We do so first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation using any projection matrix in Section~\ref{sec:oblique}.

@@

In other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy. In particular, this measure is the square root of the sum of squared forecast errors of \emph{all} variables in the hierarchy. Consequently, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy. Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT\@. It is to oblique projections that we now turn our attention.

@@

One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the square root of the sum of squared errors of \emph{all} variables in the hierarchy. A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally. For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series. Even when two series are on a similar scale, series that are more predictable or less variable will tend to be down-weighted by simply aggregating squared errors. An even more sophisticated understanding may take the correlation between series into account. All of these considerations lead towards {\color{blue} thinking of distance and loss functions based on $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, where $\bm{W}$ is a symmetric matrix assumed to be invertible.  In the geometry defined by the norm $||.||_{\bm{W}^{-1}}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$, an orthogonal projection has the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$.}

One way to understand the generalied Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$. This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$. The transformed reconciled forecast results from an orthogonal projection in the transformed space since
\begin{align*}
  \tilde{\bm{y}}^*
    & = \bm{W}^{-1/2}\tilde{\bm{y}} \\
    & = \bm{W}^{-1/2}\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}} \\
    & = \bm{S}^*(\bm{S}^{*'}\bm{S}^*)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
\end{align*}

@@

The implication of Theorem~\ref{th:gdistred} is that if the objective function is {\color{blue} a priori as} some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.  {\color{blue}  This result does not depend on the covariance of forecast errors except in the special case where $\bm{W}$ is set to this covariance matrix.}

@@

{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}. While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different} optimality property. \citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts{\color{blue}, i.e, $\textrm{tr}(E(y_t-\tilde{y}_t)(y_t-\tilde{y}_t)')$,} is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}. Here, {\color{blue}$\bm{\Sigma}$} is the forecast error covariance matrix where errors come from using the base forecasts. Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.  {\color{blue} In the subsequent discussion MinT will refer to any method that attempts to estimate $\bm{\Sigma}$, specific estimators can be found in \cite{WicEtAl2019} and also \cite{NysEtAl2019}.}

@@

After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} WLS, MinT and GMinT.   For MinT and GMinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.  That is $\bm{\Sigma} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
	\begin{equation*}
	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
	\end{equation*}
	where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.  For WLS and GMinT, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$ CHANGE DEPENDING ON FINAL CHOICE OF W.  For both loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.

@@

Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased. {\color{blue} In addition to the total squared error defined in Equation~\ref{eq:tse}, the total error (TE) is used to measure bias and is computed as
\begin{equation*}
\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\quad \textrm {and}\quad \textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,.
\end{equation*}
Table~\ref{tab:Results_MSE} reports the relative mean total error (RMTE) and relative mean total error (RMTSE) defined as  
\begin{equation*}
\textrm{RMTE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TE}^{\textrm{Base}}_t}\quad \textrm {and}\quad \textrm{RMTSE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,,
\end{equation*}
where $\textrm{TE}^{\textrm{Base}}_t$ and $\textrm{TSE}^{\textrm{Base}}_t$ are the total error and total squared error of the biased base forecasts at replication $t$.  Stars indicate that the results are significantly different from the biased base forecasts using a DETAILS OF TEST HERE.  Results are shown for $1$-step-ahead forecasts and} as was the case with Section~\ref{sec:comparebase}, the conclusions that follow extend almost identically to longer forecast horizons. {\color{blue} These are provided in an online supplement}.

>>>>

The past decade has seen rapid development in methodologies for forecasting time series that follow a hierarchical aggregation structure. Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted to ensure coherence with aggregation constraints. Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples. {\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating reconciliation as an optimisation problem to minimise weighted squared errors between coherent and incoherent forecasts}.  The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model. In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation. This allows us to develop novel proofs and a clearer understanding of the interplay between forecast bias and reconciliation methods.

@@

In contrast to these methods, \citet{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as \emph{base} forecasts. Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment. A framework was proposed whereby the aggregation constraints were expressed in a regression model for the base forecasts. The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts. This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep[see for example][among others]{Athanasopoulos2009, AthEtAl2017, WicEtAl2019}. Some theoretical insight into the performance of forecast reconciliation methods has been provided by \citet{VanErven2015a} and \citet{WicEtAl2019}. Both papers provide a proof that reconciliation is guaranteed to improve base forecasts. The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method. This is optimal in a {\color{blue} different} sense of minimising the trace of the reconciled forecast error covariance matrix under the assumption that the base forecasts are unbiased.

Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem. In this setting, we show that reconciled forecasts have a number of attractive properties when they are obtained via projections. We believe that this is clearer and more intuitive than explanations based on regression modelling. In addition to casting existing results in a new light, the geometric interpretation also allows us to derive {\color{blue}four} new important results.

First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints. As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling. Second, {\color{blue} we provide a new proof of the results that reconciled forecasts dominate unreconciled forecasts, for a certain class of loss functions. The projection that achieves this need only depend on the loss function and not on the dependence in forecast errors.}  Futhermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.  {\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors.  While this is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}, we provide new intuition and also establish that the result applies to a more general class of loss functions.  Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased. A natural question that arises is what to do in the case of biased reconciled forecasts. Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation. This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.

The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines hierarchical time series in a way that does not depend on any notion of bottom-level series. Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes proofs that make the optimality properties of different reconciliation methods clear. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions {\color{blue}for} forecast reconciliation.

@@

In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.
\begin{itemize}
\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e. the base and reconciled forecasts should be `close'.  {\color{blue} This property is particularly emphasised by \cite{NysEtAl2019}}
\item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.  {\color{blue} This property is particularly emphasised by \cite{WicEtAl2019}.}
\end{itemize}

To address the first of these properties we make the concept of closeness more concrete by considering the Euclidean distance between the base forecast $\hat{\bm{y}}_{t+h|t}$ and the reconciled forecast $\tilde{\bm{y}}_{t+h|t}$. A property of an orthogonal projection is that the distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$. {\color{blue} For Euclidean distance this can be expressed as minimising $\|\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.

The {\color{blue} second property is concerned with $\|{\bm{y}}_{t+h}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ relative to $\|{\bm{y}}_{t+h}-\hat{\bm{y}}_{t+h|t}\|$.  The idea is} that reconciled forecasts should always be closer to the target than base forecasts and was touched upon in Section 2.3 of \citet{WicEtAl2019}. The discussion in that paper focuses on the {\color{blue} special} case of MinT\@. Here we provide a new explicit proof of that result. We do so first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation using any projection matrix in Section~\ref{sec:oblique}.

@@

In other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy. In particular, this measure is the square root of the sum of squared forecast errors of \emph{all} variables in the hierarchy. Consequently, while forecast improvement is guaranteed for the hierarchy overall, {\color{blue} forecast errors are treated equally across all series} and reconciliation can {\color{blue} still} lead to less accurate forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy. Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT\@. {\color{blue} We now turn our attention to the way oblique projections can address both of these shortcomings} .

@@

One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the square root of the sum of squared errors of \emph{all} variables in the hierarchy. A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally. For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series. Even when two series are on a similar scale, series that are more predictable or less variable will tend to be down-weighted by simply aggregating squared errors. An even more sophisticated understanding may take the correlation between series into account.  {\color{blue} Finally, the context of the forecast problem itself may suggest a loss function, for instance in our tourism example an appropriate loss function may weight forecast errors by average tourism expenditure in each reason}. All of these considerations lead towards {\color{blue} thinking of distance and loss functions based on $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, where $\bm{W}$ is a symmetric matrix assumed to be invertible.  In the geometry defined by the norm $||.||_{\bm{W}^{-1}}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$. }

One way to understand the generalied Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$. This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$. {\color{blue} An orthogonal projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, is an} orthogonal projection in the transformed space since
\begin{align*}
  \tilde{\bm{y}}^*
    & = \bm{W}^{-1/2}\tilde{\bm{y}} \\
    & = \bm{W}^{-1/2}\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}} \\
    & = \bm{S}^*(\bm{S}^{*'}\bm{S}^*)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
\end{align*}

@@

The implication of Theorem~\ref{th:gdistred} is that if the loss function is {\color{blue} given a priori as total sum of squared errors in some linearly transformed space,} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.  {\color{blue}  This result does not depend on the covariance of forecast errors except in the special case where $\bm{W}$ is set to this covariance matrix.}

@@

{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}. While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different} optimality property. \citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts{\color{blue}, i.e, $\textrm{tr}(E(\bm{y}_t-\tilde{\bm{y}}_t)(\bm{y}_t-\tilde{\bm{y}}_t)')$,} is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}. Here, {\color{blue}$\bm{\Sigma}$} is the forecast error covariance matrix where errors come from using the base forecasts. Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.  {\color{blue} In the subsequent discussion MinT will refer to any method that attempts to estimate $\bm{\Sigma}$, specific estimators can be found in \cite{WicEtAl2019} and also \cite{NysEtAl2019}.}

@@

After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} WLS and MinT.   For MinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.  That is $\bm{\Sigma} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
	\begin{equation*}
	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
	\end{equation*}
	where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.  For WLS, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$ CHANGE DEPENDING ON FINAL CHOICE OF W.  For both loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.

@@

Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased. {\color{blue} In addition to the total squared error defined in Equation~\ref{eq:tse}, the total error (TE) is used to measure bias and is computed as
\begin{equation*}
\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\,.
\end{equation*}
Table~\ref{tab:Results_MSE} reports the relative mean total error (RMTE) and relative mean total error (RMTSE) defined as  
\begin{equation*}
\textrm{RMTE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TE}^{\textrm{Base}}_t}\quad \textrm {and}\quad \textrm{RMTSE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,,
\end{equation*}
where $\textrm{TE}^{\textrm{Base}}_t$ and $\textrm{TSE}^{\textrm{Base}}_t$ are the total error and total squared error of the biased base forecasts at replication $t$.  Stars indicate that the results are significantly different from the biased base forecasts using a DETAILS OF TEST HERE.  Results are shown for $1$-step-ahead forecasts and} as was the case with Section~\ref{sec:comparebase}, the conclusions that follow extend almost identically to longer forecast horizons. {\color{blue} These are provided in an online supplement}.
